\plaintitle

### 2016-08-11 drafts/labor/introduction.tex
notes were in the wrong file :x
various additional notes and a fix with some colors and todonotes or something

% \usepackage[style=alphabetic]{biblatex}
\begin{document}

\newcommand{\note}[1]{\onlyinsubfile{\ali{#1}}}

@@

% Broadly, this work has imagined the various applications of ``gig''--based work,
% and making it work for ``requesters''
% --- academics, industries, and to some extent end--users
% who might benefit from the product of crowd--powered work
% \cite{hong2015group,jonBrelig,paolacci2010running}.
% % ??? -->
% Since then,
% the application of digitally mediated environments acting as rapid ``hiring halls''
% for on--demand tasks
% has found purchase far beyond the context of ``information work'' like Amazon Mechanical Turk (AMT);
% livery services (Uber), cleaning (Handy), and various other services (TaskRabbit)
% % parentheticals giving examples?
% have garnered the interest of both industry and research.

@@

% Bringing this broader body of work together, perhaps we can think of this as documenting the ``fallout'' of on--demand labor;
% workers increasingly expressing frustration with the disenfranchisement of the work--flows pioneered by researchers in the decade leading up till now,
% and researchers beginning to appreciate the unforeseen costs of transient labor and the impacts both on the work and the workers.

% \note{this probably doesn't belong here but i need to put it somewhere!}

% From a wide range of academic and industrial perspectives
% and increasingly identifying the many stakeholders in digitally mediated work,
The extant body of work has ostensibly sought to answer one underlying question:
What does the future hold for work and those that do it? % expand on ...?
Researchers have offered their input on this open question along three major threads of scholarship:
% the driving motivation behind much of the research in this space has led us to ask,
% at a high level, three important questions:
\begin{enumerate}
  \item What are the limits of crowdsourcing?
  Perhaps more tightly constrained,
  what can and cannot be done by crowd workers?
  % (what are the \textbf{complexity limits}) \note{(hospitals at high level?) -- team scaffolds} \note{why is there a high limit? is that different with crowds?}
    \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,embracingErrorKrishna,Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364};
  \item What forms of work design, and worker management and arrangement, are viable?
  % \note{time in motion studies; job design; } or is this more about managers, coops, etc...
    \cite{bernsteinSoylent,sensitiveTasks,LykourentzouPersonalityMatters,KucherbaevReLauncher,Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item What will work and the place of work look like for the workers?
    \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,whyWouldAnyoneBrewer,takingAHITMcInnis}
    % \note{these questions are all a little guilty of vagueness but this feels especially ``meh''}
\end{enumerate}

@@

% so CW?
% mechanism/limitation in pw?
% differences in cw? tech/access to intelligence?
% predicted outcome then? -> decompose effort/expertise access
% possible quirks/diffs?

% These bodies of literature have conversed,
% and indeed begun to identify that their theories are interrelated in some way,
% but thus far a convincing model for making sense of
% --- let alone predicting ---
% the phenomena in on--demand labor has proven elusive.
% For instance, 
% making sense of why workers on AMT (or ``Turkers'') are frustrated with their workplace
% is understandable in its own context, but
% the relationship between the work itself (``turking'')
% and the myriad social outcomes has only briefly been explored
% \cite{crowdcollab}.

We offer a framing for crowd work spanning the aforementioned industries
collectively as a contemporary instantiation of ``piecework''.
Piecework as a metaphor for the type of work at hand is not new.
Indeed,
\citeauthor{crowdworkFuture}
in
\citeauthor{crowdworkFuture}
referenced crowd work as ``piecework'' briefly
as a loose analogy to the form of work emerging at the time
% but not given as much weight as it perhaps could have been
\cite{crowdworkFuture}.
% ``Piecework'' here makes use of
% a term historically used to describe work done in the home,
% in manageable tasks,
% often involving clear instructions
% and payment only for work completed, not work done
% (the differentiation then being that
% one would be paid for the \textit{output} of the work,
% not the \textit{duration}).

% This framing prompts us to note several immediately apparent similarities:
% \begin{inlinelist}
%   \item this form of work began in the home
%   \item the worker is paid for each discrete piece of work done, regardless of time or effort; and
%   \item the worker's status
%   (not only socially, but also economically)
%   is ambiguous, or at least the subject of some controversy.
% \end{inlinelist}

@@

We'll look at a broad range of cases under a number of major themes
we propose as broadly describing the types of research being done in crowd work
and more generally in what we argue is contemporary piecework.
After validating this lens as a way of reasoning about on--demand labor,
we'll attempt to use this perspective to suggest areas of research worth anticipating,
and developments we should expect to see in the maturation of digitally mediated work.
Finally, we will offer design implications based on this research\dots
% \note{???}

\note{
\textbf{notes/what i want to get across\dots}

@@

\onlyinsubfile{
  \balance{}
  % \bibliography{references}
  \printbibliography
}

>>>>

\begin{document}

@@

@@

The extant body of work has ostensibly sought to answer one underlying question:
What does the future hold for work and those that do it? % expand on ...?
Researchers have offered their input on this open question along three major threads of scholarship:
\begin{enumerate}
  \item What are the limits of crowdsourcing?
  Perhaps more tightly constrained,
  what can and cannot be done by crowd workers?
    \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,embracingErrorKrishna,Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364};
  \item What forms of work design, and worker management and arrangement, are viable?
    \cite{bernsteinSoylent,sensitiveTasks,LykourentzouPersonalityMatters,KucherbaevReLauncher,Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item What will work and the place of work look like for the workers?
    \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,whyWouldAnyoneBrewer,takingAHITMcInnis}
\end{enumerate}

@@

We offer a framing for crowd work spanning the aforementioned industries
collectively as a contemporary instantiation of ``piecework''.
Piecework as a metaphor for the type of work at hand is not new.
Indeed,
\citeauthor{crowdworkFuture} in \citeauthor{crowdworkFuture}
referenced crowd work as ``piecework'' briefly
as a loose analogy to the form of work emerging at the time
\cite{crowdworkFuture}.

@@

We'll look at a broad range of cases under a number of major themes
we propose as broadly describing the types of research being done in crowd work
and more generally in what we argue is contemporary piecework.
After validating this lens as a way of reasoning about on--demand labor,
we'll attempt to use this perspective to suggest areas of research worth anticipating,
and developments we should expect to see in the maturation of digitally mediated work.
Finally, we will offer design implications based on this research\dots

\endnote{
\textbf{notes/what i want to get across\dots}

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
  \theendnotes
}
